---
title: "LogisticRegression Package Vignette"
author: "Drew Beckwith, Kaley Fulcher"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Vignette for the `LogisticRegression` Package

This package is located in the GitHub Repository titled `FinalProject_1` and was created by Drew Beckwith and Kaley Fulcher.

The package can compute the estimator beta hat, create bootstrap confidence intervals, plot fitted logistic curves, output the Confusion Matrix, and output various metrics. 

To illustrate the abilities of this package, we will use the `adult.csv` data provided. We'll begin by uploading the package, the data, and altering the data format to fit our needs.


```{r cars, include = T}
devtools::install_github("https://github.com/AU-R-Data-Science/FinalProject_1")
library(FinalProject1)
adult <- read.csv("adult.csv", sep=";")
head(adult)
#reformatting
colsToChange <- colnames(adult)
colsToChange[16] <- "salary"
colsToChange[6] <- "educationNum"
colsToChange[14] <- "hoursPerWeek"
colnames(adult) <- colsToChange
colnames(adult)
adult["salary"] <- lapply(adult["salary"],function(x) substring(x, 2))
adult$salary <- replace(adult$salary, adult$salary == "<=50K", 0)
adult$salary <- replace(adult$salary, adult$salary == ">50K", 1)

int <- rep(1, nrow=nrow(adult))
x <- cbind(adult$age, adult$hoursPerWeek)
```

## Regression

Let's look at, for example, how the age and hours per week affect salary.

```{r optim}
colnames(x) <- c("age","hoursPerWeek")
datatoTest <- list("y" = matrix(as.numeric(adult$salary), nrow=nrow(adult)), "X" = x)
logisticRegression(datatoTest$y, datatoTest$X)

```

This function gives you a large amount of information: the estimator, the confusion matrix, etc. 

If a user doesn't need all this information, they can pick and choose what information they want by using one of the embedded/built-in functions. 

For example, the user can show just the boostrap:

```{r bootstrap}

bootStrapLogisticRegression(B = 5, alpha = .05, datatoTest$y, datatoTest$X)


```

Or, the user can choose specific metrics to plot:

```{r metrics}

plotMetric(datatoTest$y, datatoTest$X, "Prevalence")

plotMetric(datatoTest$y, datatoTest$X, "Accuracy")

plotMetric(datatoTest$y, datatoTest$X, "Sensitivity")

plotMetric(datatoTest$y, datatoTest$X, "Specificity")

plotMetric(datatoTest$y, datatoTest$X, "False Discovery Rate")

plotMetric(datatoTest$y, datatoTest$X, "Diagnostic Odds Ratio")




```




